### 2013-06-17 Tex/chapters/model.tex
Caption ergänzt, Bilder umsortiert, Formulierung geändert

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    All here mentioned graph types are \emph{proximity graphs}. They are
    connecting nodes which are by some metric near to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships, like the Ising model
    which will be described in more detail in section
    \ref{ssec:isingmodel}.\\
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the lunes][]{
                \label{sfig:lunes:def}
                \input{images/GG_RNG_def}
        }
        \subfigure[Gabriel graph example][]{
                \label{sfig:lunes:gg}
                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
        }
        \subfigure[Relative Neighborhood graph example][]{
                \label{sfig:lunes:rng}
                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
        }
        \caption[Gabriel - and Relative Neighborhood Graph]
                {\subref{sfig:lunes:def} Lunes of Gabriel Graph (red)
                    and Relative Neighborhood Graph (blue and red).
                 \subref{sfig:lunes:gg} Example of a Gabriel Graph on
                    periodic boundary conditions. Periodic nodes are
                    dashed.
                 \subref{sfig:lunes:def} Example of a Relative
                    Neighborhood Graph on periodic boundary conditions.
                    Periodic nodes are dashed.}
        \label{fig:lunes}

@@

    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {\subref{sfig:collapse_s_0}
                 \subref{sfig:binder_fit_s_0} Binder cumulant fitted with
                    polynom of degree 4 in vincinity of \(T_c\)
                    (the errorbars are too small to see)}
        \label{fig:binder_fit_s_0}
    \end{figure}
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a polynom of degree 4 is fitted to \(g\) in vicinity of
    the intersection.
    In fig. \ref{fig:binder_fit_s_0} such a fit is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
    To determine \(T_c\) the intersections are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.269(1)\), which
    is in very good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\

>>>>

%~ \subsubsection{Graphs}
    %~ A graph is a set of nodes \(V\) and edges \(E\).
\subsection{Gabriel- and Relative Neighborhood Graph}
\label{ssec:graphtypes}
    All here mentioned graph types are \emph{proximity graphs}. They are
    connecting nodes which are by some metric near to each other.
    Hence they are suited to generalize problems defined on regular
    lattices with nearest neighbor relationships, like the Ising model
    which will be described in more detail in section
    \ref{ssec:isingmodel}.\\
    The Gabriel Graph \cite{Gabriel1969} is a subgraph of the
    Delaunay Triangulation. Two nodes \(i\) and \(j\) with distance
    \(d_{ij}\) are connected with an edge if a circle with it's
    center on the middlepoint between \(i\) and \(j\) and radius
    \(r = \frac d 2\) contains no other nodes. This area will be
    called \emph{lune} in the following. See also Figure
    \ref{fig:lunes}\subref{sfig:lunes:def}.\\
    The Relative Neighborhood Graph \cite{Toussaint1980} is a
    subgraph of the Gabriel Graph. Two nodes \(i\) and \(j\) with
    distance \(d_{ij}\) are connected if no other node is in the
    \emph{lune}. The lune is defined as the intersection of two
    circles with radius \(r = d\) and centers on \(i\) and \(j\).
    See also Figure \ref{fig:lunes}\subref{sfig:lunes:def}.
    \begin{figure}[htbp]
        \centering
        \subfigure[Definition of the lunes][]{
                \label{sfig:lunes:def}
                \input{images/GG_RNG_def}
        }
        \subfigure[Relative Neighborhood graph example][]{
                \label{sfig:lunes:rng}
                \includegraphics[width=0.3\textwidth]{images/RNG/L12S03.pdf}
        }
        \subfigure[Gabriel graph example][]{
                \label{sfig:lunes:gg}
                \includegraphics[width=0.3\textwidth]{images/GG/L12S03.pdf}
        }
        \caption[Gabriel - and Relative Neighborhood Graph]
                {\subref{sfig:lunes:def} Lunes of Relative Neighborhood
                    Graph (hatched region) and
                    Gabriel Graph (cross hatched region)
                 \subref{sfig:lunes:def} Example of a Relative
                    Neighborhood Graph on periodic boundary conditions.
                    Periodic nodes are dashed.
                 \subref{sfig:lunes:gg} Example of a Gabriel Graph on
                    periodic boundary conditions. Periodic nodes are
                    dashed.
                }
        \label{fig:lunes}

@@

    %~ [Erklärung autoscale]
    %~ [Am besten hier direkt die ganze Auswertung rein]
    %~ [weiter ausarbeiten] [sagen, dass man für zwei/drei sigma die exponenten reproduziert hat].\\
    \begin{figure}[htbp]
        \centering
        \subfigure[Example of a Binder cumulant to determine the critical temperature][]{
                \label{sfig:binder_fit_s_0}
                \includegraphics[width=0.47\textwidth]{plots/binder_fit_s_0}
        }
        \subfigure[Example of a datacollapse to determine critical exponents][]{
                \label{sfig:collapse_s_0}
                \includegraphics[width=0.47\textwidth]{plots/collapse_s_0}
        }
        \caption[Examples of determining critical temperature and exponents]
                {\subref{sfig:binder_fit_s_0} Binder cumulant interpolated
                    with cubic splines (the errorbars are too small to see)
                 \subref{sfig:collapse_s_0} Collapse of the Binder cumulant
                }
        \label{fig:binder_fit_s_0}
    \end{figure}
    Though if one is just interested in the critical Temperature, an
    easier approach is to find the intersections of the Binder cumulants
    \(g = 3-\frac{\avg{m^4}}{2\avg{m^2}^2}\) \cite{Binder1981} of different
    system sizes \(L=\sqrt N\).
    Therefore a cubic spline interpolation is calculated\footnote{created using the \texttt{scipy.interpolate} tools \cite{scipy2001}}
    for the measured points.
    In fig. \ref{fig:binder_fit_s_0} such an interpolation is plotted for
    \(\sigma=0\). The cumulants intersect at \(\approx 2.27\).
    To determine \(T_c\) the intersections\footnote{found using the \texttt{scipy.optimize} tools \cite{scipy2001}}
    are averaged and the standard
    error is calculated. In this case one gets \(T_c = 2.2689\pm0.0002\), which
    is in good agreement with the exact solution
    \(T_c = 2.2691...\) \cite{Onsager1944}.\\
